Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2024-06-19 manuscript/manuscript.tex
changed table to rejection rate instead of ratio

\begin{table}[tbp]
\centering
\caption{Empirical sizes (ratio of rejection rate to significance level)
for the test that sample follows its true distribution family for
different values of AR(1) coefficient and for different 
significance levels.
\eds{Not sure if it will help presentation or interpretation, but you could
  consider presenting the values inside the table as estimated size/true size}
\mc{addressed}
\eds{I meant reporting the ratio, e.g, dividing all values currently in the    first row by 0.01, dividing all values in the second row by 0.05. Sometimes this
	is helpful if there is a conservative or liberal pattern, which there seems
	to be as $|\tau|$ increases away from zero, but it may be fine to leave it as
	is.}\mc{how does this look?}
\jy{Once finalized, don't forget to update the caption.}
    }
\label{table:size}
\begin{tabular}{lllrrrrrrr}
  \toprule
$F(\cdot; \theta)$ & $n$ & $\alpha$ & $\tau = -0.75$ & $\tau = -0.5$ & $\tau = -0.25$ 
& $\tau = 0$ & $\tau = 0.25$ & $\tau = 0.5$ & $\tau = 0.75$ \\ 
  \midrule
{$N(8,8)$} & {100} & 0.01 & 5.210 & 1.240 & 1.120 & 1.060 & 1.140 & 1.580 & 5.630 \\ 
& & 0.05 & 2.940 & 1.256 & 1.090 & 1.096 & 1.150 & 1.450 & 3.410 \\ 
& & 0.10 & 2.277 & 1.186 & 1.147 & 1.072 & 1.154 & 1.424 & 2.714 \\ 
& {200} & 0.01 & 4.390 & 1.130 & 0.900 & 1.140 & 1.090 & 1.380 & 5.900 \\ 
& & 0.05 & 2.556 & 1.120 & 1.020 & 1.064 & 1.092 & 1.382 & 3.452 \\ 
& & 0.10 & 2.080 & 1.123 & 1.069 & 1.086 & 1.051 & 1.332 & 2.650 \\ 
& {400} & 0.01 & 3.240 & 1.070 & 0.990 & 1.080 & 0.970 & 1.260 & 4.670 \\ 
& & 0.05 & 2.032 & 1.000 & 0.994 & 1.120 & 0.978 & 1.184 & 2.836 \\ 
& & 0.10 & 1.734 & 1.023 & 1.002 & 1.089 & 1.017 & 1.192 & 2.232 \\ 
& {800} & 0.01 & 2.520 & 0.900 & 0.980 & 1.110 & 1.020 & 1.350 & 3.540 \\ 
& & 0.05 & 1.766 & 1.008 & 0.972 & 0.956 & 0.962 & 1.236 & 2.438 \\ 
& & 0.10 & 1.555 & 1.026 & 0.986 & 0.961 & 0.997 & 1.206 & 2.044 \\ [1ex]
{$\Gamma(8,1)$} & {100} & 0.01 & 4.880 & 1.420 & 1.170 & 1.240 & 1.110 & 1.610 & 5.760 \\ 
  & & 0.05 & 2.850 & 1.282 & 1.222 & 1.170 & 1.178 & 1.464 & 3.374 \\ 
  & & 0.10 & 2.241 & 1.224 & 1.147 & 1.175 & 1.150 & 1.375 & 2.679 \\ 
  & {200} & 0.01 & 4.080 & 1.000 & 0.890 & 1.220 & 1.160 & 1.430 & 6.080 \\ 
  & & 0.05 & 2.510 & 1.118 & 1.014 & 1.068 & 1.116 & 1.290 & 3.380 \\ 
  & & 0.10 & 1.991 & 1.105 & 1.022 & 1.048 & 1.072 & 1.233 & 2.664 \\ 
  & {400} & 0.01 & 3.140 & 0.970 & 1.140 & 0.940 & 1.030 & 1.310 & 4.300 \\ 
  & & 0.05 & 2.004 & 0.964 & 1.042 & 1.062 & 1.122 & 1.236 & 2.808 \\ 
  & & 0.10 & 1.697 & 1.025 & 1.066 & 1.018 & 1.100 & 1.177 & 2.232 \\ 
  & {800} & 0.01 & 2.490 & 0.920 & 1.130 & 1.120 & 1.000 & 1.130 & 3.810 \\ 
  & & 0.05 & 1.804 & 0.976 & 1.064 & 1.022 & 1.086 & 1.196 & 2.474 \\ 
  & & 0.10 & 1.561 & 1.024 & 1.072 & 1.034 & 1.067 & 1.177 & 1.997 \\ 
   \bottomrule
\end{tabular}
\end{table}

For a closer scrutiny on whether the test holds its size at commonly used
significance levels 0.01, 0.05, and 0.10, Table~\ref{table:size}
summarizes the empirical sizes of the tests based on 10000 replicates.
The agreement between the empirical sizes and the nominal size
improves as sample size improves, as expected. For $\tau = -0.75$
and $\tau = 0.75$, a sample size as large as 800 is still not sufficient for the
agreement to be reached. For weaker dependence levels, our approach is working
for $-0.25 < \tau < 0.25$ for $n = 100$. However, a larger sample size seems 
necessary, greater than 400 perhaps, for $\tau$ as strong as $0.5$. To 
summarize, for weaker dependence, our method works without need for a 
particularly large sample size, whereas for moderate dependence, a larger sample
size is required. When the agreement is not met, the empirical size is 
usually larger than 1, which indicates that the test is too liberal. In
other words, the test rejects the null hypothesis more often than it should.
For practical situations with a $\tau$ of magnitude 0.5 or
lower, it is still reasonable to recommend our method with $n \ge 400$.
This recommendation echoes the high sample size requirement for
confidence intervals constructed with block bootstrapping in
estimating location, scale, and autocorrelation parameters of
stationary series~\citep{chandy2024sample}.

>>>>

\begin{table}[tbp]
\centering
\caption{Empirical sizes or rejection rates
for the test that sample follows its true distribution family for
different values of AR(1) coefficient and for different 
significance levels.
\eds{Not sure if it will help presentation or interpretation, but you could
  consider presenting the values inside the table as estimated size/true size}
\mc{addressed}
\eds{I meant reporting the ratio, e.g, dividing all values currently in the    first row by 0.01, dividing all values in the second row by 0.05. Sometimes this
	is helpful if there is a conservative or liberal pattern, which there seems
	to be as $|\tau|$ increases away from zero, but it may be fine to leave it as
	is.}\mc{how does this look?}
\jy{Once finalized, don't forget to update the caption.}
    }
\label{table:size}
\begin{tabular}{lllrrrrrrr}
  \toprule
$F(\cdot; \theta)$ & $n$ & $\alpha$ & $\tau = -0.75$ & $\tau = -0.5$ & $\tau = -0.25$ 
& $\tau = 0$ & $\tau = 0.25$ & $\tau = 0.5$ & $\tau = 0.75$ \\ 
  \midrule
{$N(8,8)$} & {100} & 0.01 & 0.0521 & 0.0124 & 0.0112 & 0.0106 & 0.0114 & 0.0158 & 0.0563 \\ 
& & 0.05 & 0.1470 & 0.0628 & 0.0545 & 0.0548 & 0.0575 & 0.0725 & 0.1705 \\ 
& & 0.10 & 0.2277 & 0.1186 & 0.1147 & 0.1072 & 0.1154 & 0.1424 & 0.2714 \\ 
& {200} & 0.01 & 0.0439 & 0.0113 & 0.0090 & 0.0114 & 0.0109 & 0.0138 & 0.0590 \\ 
& & 0.05 & 0.1278 & 0.0560 & 0.0510 & 0.0532 & 0.0546 & 0.0691 & 0.1726 \\ 
& & 0.10 & 0.2080 & 0.1123 & 0.1069 & 0.1086 & 0.1051 & 0.1332 & 0.2650 \\ 
& {400} & 0.01 & 0.0324 & 0.0107 & 0.0099 & 0.0108 & 0.0097 & 0.0126 & 0.0467 \\ 
& & 0.05 & 0.1016 & 0.0500 & 0.0497 & 0.0560 & 0.0489 & 0.0592 & 0.1418 \\ 
& & 0.10 & 0.1734 & 0.1023 & 0.1002 & 0.1089 & 0.1017 & 0.1192 & 0.2232 \\ 
& {800} & 0.01 & 0.0252 & 0.0090 & 0.0098 & 0.0111 & 0.0102 & 0.0135 & 0.0354 \\ 
& & 0.05 & 0.0883 & 0.0504 & 0.0486 & 0.0478 & 0.0481 & 0.0618 & 0.1219 \\ 
& & 0.10 & 0.1555 & 0.1026 & 0.0986 & 0.0961 & 0.0997 & 0.1206 & 0.2044 \\ [1ex]
{$\Gamma(8,1)$} & {100} & 0.01 & 0.0488 & 0.0142 & 0.0117 & 0.0124 & 0.0111 & 0.0161 & 0.0576 \\ 
  & & .05 & 0.1425 & 0.0641 & 0.0611 & 0.0585 & 0.0589 & 0.0732 & 0.1687 \\ 
  & & 0.10 & 0.2241 & 0.1224 & 0.1147 & 0.1175 & 0.1150 & 0.1375 & 0.2679 \\ 
  & {200} & 0.01 & 0.0408 & 0.0100 & 0.0089 & 0.0122 & 0.0116 & 0.0143 & 0.0608 \\ 
  & & 0.05 & 0.1255 & 0.0559 & 0.0507 & 0.0534 & 0.0558 & 0.0645 & 0.1690 \\ 
  & & 0.10 & 0.1991 & 0.1105 & 0.1022 & 0.1048 & 0.1072 & 0.1233 & 0.2664 \\ 
  & {400} & 0.01 & 0.0314 & 0.0097 & 0.0114 & 0.0094 & 0.0103 & 0.0131 & 0.0430 \\ 
  & & 0.05 & 0.1002 & 0.0482 & 0.0521 & 0.0531 & 0.0561 & 0.0618 & 0.1404 \\ 
  & & 0.10 & 0.1697 & 0.1025 & 0.1066 & 0.1018 & 0.1100 & 0.1177 & 0.2232 \\ 
  & {800} & 0.01 & 0.0249 & 0.0092 & 0.0113 & 0.0112 & 0.0100 & 0.0113 & 0.0381 \\ 
  & & 0.05 & 0.0902 & 0.0488 & 0.0532 & 0.0511 & 0.0543 & 0.0598 & 0.1237 \\ 
  & & 0.10 & 0.1561 & 0.1024 & 0.1072 & 0.1034 & 0.1067 & 0.1177 & 0.1997 \\ 
   \bottomrule
\end{tabular}
\end{table}

For a closer scrutiny on whether the test holds its size at commonly used
significance levels 0.01, 0.05, and 0.10, Table~\ref{table:size}
summarizes the empirical sizes of the tests based on 10000 replicates.
The agreement between the empirical sizes and the nominal size
improves as sample size improves, as expected. For $\tau = -0.75$
and $\tau = 0.75$, a sample size as large as 800 is still not sufficient for the
agreement to be reached. For weaker dependence levels, our approach is working
for $-0.25 < \tau < 0.25$ for $n = 100$. However, a larger sample size seems 
necessary, greater than 400 perhaps, for $\tau$ as strong as $0.5$. To 
summarize, for weaker dependence, our method works without need for a 
particularly large sample size, whereas for moderate dependence, a larger sample
size is required. When the agreement is not met, the empirical size is 
usually larger than the nominal size, which indicates that the test is too liberal. 
In
other words, the test rejects the null hypothesis more often than it should.
For practical situations with a $\tau$ of magnitude 0.5 or
lower, it is still reasonable to recommend our method with $n \ge 400$.
This recommendation echoes the high sample size requirement for
confidence intervals constructed with block bootstrapping in
estimating location, scale, and autocorrelation parameters of
stationary series~\citep{chandy2024sample}.
